---
title: "Instructor Feedback Questions 1 to 3"
author: "Katrin"
date: "10/18/2018"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(ggplot2)
library(dplyr)
library(readr)
```

## What Operation system do participants have?
```{r}
pre_os <- readr::read_csv('../data/20181002-pre-os-no-open.csv', na = '<NA>')
```

```{r}
# change order of factor variable os and rename factors ('Not sure' does not contain real space, more steps in renaming ...!)
# convert os to factor
pre_os$os <- as.factor(pre_os$os)
# rename levels of os, combine 'NA' and 'Not sure' to 'unknown'
levels(pre_os$os) <- c('Mac OS', 'Linux', 'unknown', 'unknown', 'Windows')
# re-order levels of os
pre_os$os <- factor(pre_os$os, levels = c('Windows', 'Mac OS', 'Linux', 'unknown'))
```

```{r}
# 1) make dataframe with counts/percentages for plotting
pre_os_pl <- pre_os %>%
  dplyr::group_by(os) %>%
  dplyr::count() %>%
  dplyr::ungroup() %>%
  dplyr::mutate(n_percent = round(100 * n/sum(n)))
```

```{r}
# prepare data for plotting
pre_os_pl <- pre_os_pl %>%
  # only show values > 2%
  dplyr::filter(n_percent > 2) %>%
  # sort os
  arrange((os))
```

```{r}
# make plot
ggplot(data = pre_os_pl, aes(x = "", y = n_percent, fill = os)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") + 
  theme_void()
```

Most participants in your workshop will have `r pre_os_pl$os[pre_os_pl$n == max(pre_os_pl$n)]` computers.

# try a different chart - waffle chart
```{r}
#devtools::install_github("hrbrmstr/waffle")
library(waffle)

waffle(pre_os_pl)
```


## What Disciplines/Domains do your participants come from?
```{r}
pre_dom <- read_csv('../data/20181002-pre-professional_profile-no-open.csv', na = '<NA>')
```


```{r}
# separate domains
domains <- pre_dom$domain %>%
  strsplit(';') %>%
  # strip quotation marks and space
  lapply(stringi::stri_trim) %>%
  unlist()
# combine some similar domains from main list
domains[domains == 'Medicine'] <- 'Biomedical or Health Sciences'
domains[domains == 'Biomedical or Health Sciences'] <- 'Medical or Health Sciences'
domains[domains == 'Earth Sciences'] <- 'Planetary Sciences (Geology, Climatology, Oceanography, etc.)'
domains[domains == 'NA'] <- 'Other'
# make a tibble with domains
domains <- dplyr::tibble(domain = domains)
```

```{r}
# make dataframe with counts/percentages
pre_dom_cnt <- domains %>%
  dplyr::group_by(domain) %>%
  dplyr::count() %>%
  dplyr::ungroup() %>%
  dplyr::mutate(n_percent = round(100 * n/sum(n)))
```

```{r}
# prepare data for plotting
# combine rare domains (<5 percent) into group Other
pre_dom_pl <- pre_dom_cnt %>%
  dplyr::mutate(domain = ifelse(n_percent >= 5, domain, 'Other')) %>%
  dplyr::group_by(domain) %>%
  dplyr::summarise(n_percent_s = sum(n_percent), n_s = sum(n)) %>%
  dplyr::ungroup() %>%
  arrange(desc(n_s))
```


```{r}
# make the plot
ggplot(data = pre_dom_pl) +
  geom_bar(aes(x = reorder(domain,n_s), y = n_percent_s), 
           stat='identity', fill = 'grey') + 
  geom_text(aes(x = domain, y = n_percent_s/2, label = n_s), 
            stat = 'identity', size = 4) + 
  coord_flip() +
  # remove padding on percentage axis, set limits
  scale_y_continuous(expand = c(0,0), 
                     limits = c(0, signif(max(pre_dom_pl$n_percent_s),1))) +
  labs(y = '% of participants', x = '') +
  theme_classic() +
  theme(axis.ticks.y = element_blank(),
        axis.line.y = element_blank(),
        axis.text.y=element_text(size = 10))
```

```{r}
# try a bubble chart
ggplot(data = pre_dom_pl) +
  geom_point(aes(x = reorder(domain,n_s), y = n_percent_s,
                 size = n_percent_s)) +
 # geom_text(aes(x = domain, y = n_percent_s/2, label = n_s), 
#            stat = 'identity', size = 4) + 
 # coord_flip() +
  # remove padding on percentage axis, set limits
#  scale_y_continuous(expand = c(0,0), 
#                     limits = c(0, signif(max(pre_dom_pl$n_percent_s),1))) +
 # labs(y = '% of participants', x = '') +
  theme_classic() +
  theme(axis.ticks.y = element_blank(),
        axis.line.y = element_blank(),
        axis.text.y=element_text(size = 10))
```

Participants in your workshop mainly have a background in `r pre_dom_pl$domain[1]`, `r pre_dom_pl$domain[2]` and `r pre_dom_pl$domain[3]`.


## What is the position/career stage of participants in your workshop?
```{r}
# separate occupation
occupation <- pre_dom$occupation %>%
  strsplit(';') %>%
  # strip quotation marks and space
  lapply(stringi::stri_trim) %>%
  unlist()
# combine some similar domains from main list
occupation[occupation == 'NA'] <- 'Other'
# make a tibble with occupations
occupation <- dplyr::tibble(occupation)
```

```{r}
# make dataframe with counts/percentages
pre_occ_cnt <- occupation %>%
  dplyr::group_by(occupation) %>%
  dplyr::count() %>%
  dplyr::ungroup() %>%
  dplyr::mutate(n_percent = round(100 * n/sum(n)))
```

```{r}
# prepare data for plotting
# combine rare domains (<5 percent) into group Other
pre_occ_pl <- pre_occ_cnt %>%
  dplyr::mutate(occupation = ifelse(n_percent >= 5, occupation, 'Other')) %>%
  dplyr::group_by(occupation) %>%
  dplyr::summarise(n_percent_s = sum(n_percent), n_s = sum(n)) %>%
  dplyr::ungroup() %>%
  arrange(desc(n_s))
```


```{r}
# make the plot
ggplot(data = pre_occ_pl) +
  geom_bar(aes(x = reorder(occupation,n_s), y = n_percent_s), 
           stat='identity', fill = 'grey') + 
  geom_text(aes(x = occupation, y = n_percent_s/2, label = n_s), 
            stat = 'identity', size = 4) + 
  coord_flip() +
  # remove padding on percentage axis, set limits
  scale_y_continuous(expand = c(0,0), 
                     limits = c(0, signif(max(pre_occ_pl$n_percent_s),1))) +
  labs(y = '% of participants', x = '') +
  theme_classic() +
  theme(axis.ticks.y = element_blank(),
        axis.line.y = element_blank(),
        axis.text.y=element_text(size = 10))
```

Most participants in your workshop will be `r pre_occ_pl$occupation[1]`, `r pre_occ_pl$occupation[2]`, and `r pre_occ_pl$occupation[3]`.

